\documentclass{article}

\usepackage[a4paper, margin=.3in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{graphicx}
\usepackage{color}

\definecolor{li}{RGB}{73,98,171}

\usepackage[colorlinks,
            linkcolor = li,
            urlcolor  = li,
            citecolor = li,
            anchorcolor = li]{hyperref}

\titleformat{\section}{\normalfont\large}{}{0em}{}
[\titlerule]

\titleformat{\subsection}{\normalfont\bfseries}{}{0em}{}

\urlstyle{rm}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\diamond$}}$}

\begin{document}
\pagenumbering{gobble}

\begingroup
\raggedright
\LARGE \bfseries Aziz Ben Ali\hfill \normalfont \large \url{grtcdr.github.io}\par
\large \href{mailto:ba.tahaaziz@gmail.com}{ba.tahaaziz@gmail.com}\par
\endgroup

\section*{Education}
\subsection*{Ecole Supérieur Privée d'Ingéniere et de Technologies \hfill \normalfont \textit{Sep. 2019 - Present}}
Studying computer science.

\section*{Employers}
\subsection*{HLi Group \normalfont --- Intern \hfill \textit{Jul. 2021 - Sep. 2021}}
Developed and optimized internal .NET web applications.

\subsection*{Thermecatex \normalfont --- Intern \hfill \textit{Aug. 2018, Sep. 2018}}
Helped develop and migrate to a new inventory system, a digitalized
version of its predecessor.

\section*{Open Source Projects}
In my spare time, I like to give back to the open source
community. I've also authored my own tools over the years:

\subsection*{\href{https://github.com/Macchina-CLI/macchina}{macchina}}
A cross-platform command-line system information fetcher with an
emphasis on performance, which has recently become a popular contender
to many well-established tools. macchina is available in numerous
official package repositories such as pkgsrc, homebrew, scoop, termux,
nixpkgs, etc.

\subsection{\href{https://github.com/Macchina-CLI/libmacchina}{libmacchina}}
A cross-platform library for retrieving system information, from
uptime and battery information, to the number of packages you have
installed.

\subsection*{\href{https://git.sr.ht/~grtcdr/citron}{citron}}
A memory-friendly tool delivering system data via on-demand
notifications, replacing the need for the traditional taskbar.

\subsection*{\href{https://git.sr.ht/~grtcdr/paspio}{paspio}}
A small library and command-line tool to measure and report password
entropy.

\section*{Skills}
\subsection*{Programming Languages}
\begin{itemize}
\item Proficient in Rust and (PL/)SQL.
\item Comfortable with PHP and shell scripting.
\item Acquainted with Python, Ruby and Java.
\end{itemize}

\subsection*{Tools}
\begin{itemize}
\item Proficient in Linux, i.e. Ubuntu and Arch. I've self-hosted an
  internet-facing server and exposed various web applications through
  it.
\item Comfortable with Git, which I use to version control my
  personal and public open source projects.
\item Previously a Vim veteran, now an Emacs devotee.
\item Uses PlantUML for any and all diagramming needs.
\end{itemize}

\subsection*{Documentation and markup languages}
\begin{itemize}
\item Proficient in Markdown.
\item Comfortable with Org Mode and HTML.
\item Acquainted with \LaTeX{} and Asciidoctor.
\end{itemize}
\end{document}
