\documentclass{article}

\usepackage[a4paper, margin=.3in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{color}

\definecolor{li}{RGB}{73,98,171}

\usepackage[colorlinks,
            linkcolor = li,
            urlcolor  = li,
            citecolor = li,
            anchorcolor = li]{hyperref}

\titleformat{\section}{\scshape\large}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalfont\bfseries}{}{0em}{}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\diamond$}}$}
\newcommand{\position}[4]{\subsection*{#1 \normalfont \hfill \textit{#2}} #4 \hfill #3}
\newcommand{\pro}[0]{Proficient in}
\newcommand{\comf}[0]{Comfortable with}
\newcommand{\acq}[0]{Acquainted with}

\begin{document}
\pagenumbering{gobble}

\begingroup
\raggedright
\hfill \large \href{https://grtcdr.github.io}{grtcdr.github.io}\par
\LARGE{\bfseries Aziz Ben Ali}
\hfill \large \href{mailto:ba.tahaaziz@gmail.com}{ba.tahaaziz@gmail.com}\par
\endgroup

\section*{Education}
\position{École Supérieur Privée d'Ingéniere et de
  Technologies}{Sep. 2019 - Present}{Tunis}{Studying computer science.}

\section*{Employers}
\position{HLi Group}{Jul. 2021 - Sep. 2021}{Intern} {Developed and
  optimized internal .NET web applications.}

\position{Thermecatex}{Aug. 2018 - Sep. 2018}{Intern} {Helped develop
  and migrate to a new inventory system, a digitalized version of its
  predecessor.}

\section*{Open Source Projects}
In my spare time, I like to give back to the open source
community. I've also authored my own tools over the years.

\subsection*{\href{https://github.com/Macchina-CLI/macchina}{macchina}}
A cross-platform command-line system information fetcher with an
emphasis on performance. macchina is available in numerous official
package repositories such as pkgsrc, homebrew, scoop, termux, nixpkgs,
and more.

\subsection{\href{https://github.com/Macchina-CLI/libmacchina}{libmacchina}}
A cross-platform library for retrieving all kinds of system
information, powering macchina, citron as well as another command-line
tool.

\subsection*{\href{https://git.sr.ht/~grtcdr/citron}{citron}}
A memory-friendly tool that delivers system data via on-demand
notifications, replacing the need for the traditional taskbar.

\subsection*{\href{https://git.sr.ht/~grtcdr/paspio}{paspio}}
A small library and command-line tool to measure and report password
entropy.

\section*{Skills}
\subsection*{Programming Languages}
\begin{itemize}
\item \pro{} Rust and (PL/)SQL.
\item \comf{} PHP and shell scripting.
\item \acq{} Python, Ruby and Java.
\end{itemize}

\subsection*{Tools}
\begin{itemize}
\item \pro{} Linux, i.e. Ubuntu and Arch. I've self-hosted an
  internet-facing server and exposed various web applications through
  it.
\item \comf{} Git, which I use to version control my personal and public projects.
\item Previously a Vim veteran, now an Emacs devotee.
\item Uses PlantUML for any and all diagramming needs.
\end{itemize}

\subsection*{Documentation and markup languages}
\begin{itemize}
\item \pro{} Markdown.
\item \comf{} Org Mode and HTML.
\item \acq{} \LaTeX{} and Asciidoctor.
\end{itemize}
\end{document}
